A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Material

### 2018-11-23 MS.tex
Read up until discussion

To compare the two methods, we converted numbers of gonotrophic cycle
(physiological age) into lifespan (chronological age) as described in
the SOM using estimates of gonotrophic cycle duration (Fig. \ref{S-fig:dissection_gonotrophicCycleRaw}). For ten species, we had enough data from both
species to make a comparison, and there was a positive correlation (not
statistically significant; Pearson correlation $\rho=0.42$, $n=10$, $p=0.23$)
between the two measures (Fig. \ref{fig:comparison}), and in only one case -- for \emph{A.
darlingi} - (Table S\#) there was a significant difference in the
time-series level LBLs.

@@

For malaria, estimates of the minimum fraction of the population that
can transmit the disease vary from \textless{}0.1\% for \emph{A.
subpictus} (from the MRR analysis, as noted above likely to be due to
the LBL substantially underestimating lifespan) to 52\% for the
drought-adapted and long-lived \emph{A sergentii.} The proportions
surviving long enough to become infectious for the two major African
malaria vectors were: for \emph{A. gambiae s.l.}: 10\% (MRR) and 27\%
(dissection); and for \emph{A. funestus s.l.}: 9\% (MRR). Using the
individual time series estimates, however, there was inconclusive
evidence for a difference in EIP between the species (MRR ANOVA:
\emph{F}\textsubscript{14,58} = 1.8, \emph{p}=0.07; MRR Kruskal-Wallis:
\(\chi_{14}^{2} = 30.2\), \emph{p} \textless{}0.01; dissection ANOVA:
\emph{F}\textsubscript{11,64} = 1.8, \emph{p}\textless{}0.01; dissection
Kruskal-Wallis: \(\chi_{11}^{2} = 38.9\), p\textless{}0.01).

>>>>

To compare the two methods, we converted numbers of gonotrophic cycle
(physiological age) into lifespan (chronological age) as described in
the SOM using estimates of gonotrophic cycle duration (Fig. \ref{S-fig:dissection_gonotrophicCycleRaw}). Table S\ref{S-tab:dissection_estimated_lifespans_chron} provides posterior summaries of chronological for the species and genera in the dissection dataset. For ten species, we had enough data from both species to make a comparison, and there was a positive correlation (not
statistically significant; Pearson correlation $\rho=0.42$, $n=10$, $p=0.23$)
between the two measures (Fig. \ref{fig:comparison}), and in only one case -- for \emph{A.
darlingi} - there was a significant difference in the
time-series level LBLs (Table S\ref{S-tab:comparison}).

@@

For malaria, estimates of the minimum fraction of the population that
can transmit the disease vary from \textless{}0.1\% for \emph{A.
subpictus} (posterior median; from the MRR analysis, as noted above likely to be due to
the LBL substantially underestimating lifespan) to 52\% (posterior median) for the
drought-adapted and long-lived \emph{A sergentii.} The proportions
surviving long enough to become infectious for the two major African
malaria vectors were: for \emph{A. gambiae s.l.}: 10\% (MRR) and 27\%
(dissection); and for \emph{A. funestus s.l.}: 9\% (MRR). Using the
individual time series estimates, there
evidence for a difference in EIP between the species (Kruskal-Wallis used due to non-normality of data; MRR:
\(\chi_{14}^{2} = 30.2\), \emph{p} \textless{}0.01; dissection: \(\chi_{11}^{2} = 38.9\), p\textless{}0.01).
